\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-01-12 presentations/popl19-01-2019/presentation.tex
New version of POPL19 presentation

\usepackage{appendixnumberbeamer}
\usepackage{xcolor}
\input{preamble}

@@

    \begin{onlyenv}<7->
      \draw (0.8, 3.7) edge[-stealth,out=25,in=155,very thick,align=center,color=white] node[above] {{\color{myred} secure}\\compilation} (4.3, 3.7);
      \draw node[rectangle,fill=white,rounded corners,draw] at (1.93,3.7) (ir1) {ir};
      \draw node[rectangle,fill=white,rounded corners,draw] at (3.15,3.7) (ir2) {ir'};
      \draw (0.8, 3.7) edge[-stealth,bend left,very thick] node[above] {} (ir1);
      \draw (ir1) edge[-stealth,bend left,very thick] node[above] {} (ir2);
      \draw (ir2) edge[-stealth,bend left,very thick] node[above] {} (4.3,3.7);
    \end{onlyenv}

@@

@@

%\section{Paper Overview}
\begin{frame}
  \frametitle{Paper Contents Overview}
  \begin{description}
  \item[Formalization of CHERI-like capability machine with linear capabilities]
  \item[\stktokens{}] a calling convention that provably guarantees local-state
    encapsulation (LSE) and well-bracketed control-flow (WBCF)
  \item[Fully-abstract overlay semantics] a novel way to prove LSE and WBCF claims
  \end{description}
\end{frame}

\section{Defining well-bracketed control flow and local state  encapsulation}

\newcommand{\drawpc}[1]{

}

\begin{frame}[fragile]
  \frametitle{Defining well-bracketed control flow and local state encapsulation}
  \begin{columns}
    \begin{column}{0.5\textwidth}
\begin{lstlisting}[language=C, escapechar=!]
!\tikz[remember picture] \node[] (a) {};!void a()       !\tikz[remember picture] \node[] (bt) {};! 
{
  !\tikz[remember picture] \node[] (pc6) {};!...
  !\tikz[remember picture] \node[] (pc7) {};!return;!\tikz[remember picture] \node[] (ret) {};!      
}               !\tikz[remember picture] \node[] (bb) {};!

void b()
{
  !\tikz[remember picture] \node[] (pc1) {};!int x = 5;
  !\tikz[remember picture] \node[] (pc2) {};!a();
  !\tikz[remember picture] \node[] (pc3) {};!...
  !\tikz[remember picture] \node[] (pc4) {};!a();
  !\tikz[remember picture] \node[] (pc5) {};!return;   
}
\end{lstlisting}
      \begin{tikzpicture}[remember picture, overlay]
%        \draw<1> node { };
        \draw<2>[decorate,decoration={brace,amplitude=6pt,raise=4pt},yshift=0pt] ($(bt) + (0,0.2)$) -- ($(bb) + (0,-0.2)$) node[xshift=0.2cm] (brace) [midway] {};
        \draw<2> node[right = -0cm of brace, text width = 3cm] {Function \texttt{a} cannot access variable \texttt{x}};

        \draw<3> ($(pc4) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc4);
        \draw<4> ($(a) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (a);
        \draw<5> ($(pc6) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc6);
        \draw<6> ($(pc7) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc7);
        \draw<7-> node[below right = of ret] (w) {\huge ?};
        \draw<7-> (ret) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202},bend left] (w);
        \draw<8> ($(pc5) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc5);
        \draw<9> ($(pc3) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc3);
      \end{tikzpicture}
    \end{column}
    \begin{column}{0.5\textwidth}
      \only<2>{Local-state encapsulation}
      \only<3->{Well-bracketed control flow}
    \end{column}
    % What is LSE and WBCF
    % Quick example?
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Desired properties of the WBCF and LSE definition}
  \begin{enumerate}
\item {\itshape Intuitive}%Should correspond to our intuition about WBCF and LSE
\item {\itshape Useful for reasoning}% we should be able to use WBCF and LSE when reasoning about correctness and security of programs using \stktokens{}.
\item {\itshape Reusable in secure compiler chains}% for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.
\item {\itshape Arguably "complete"}% the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. 
%\item {\itshape potentially scalable}% although dynamic code generation and multi-threading are currently out of scope, the formalization should, at least potentially, extend to such settings.
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Overlay Semantics}

\begin{tabular}{p{3.2cm} p{3.2cm}}
\begin{lstlisting}[basicstyle=\tiny\ttfamily,escapechar=!]
   !\tikz[remember picture] \node[] (srccodetl) {};!move  rtmp1 42
   !\tikz[remember picture] \node[] (calltl) {};!store rstk rtmp1
    cca   rstk -1
    geta  rtmp1 rstk
    cca   rretc 5      !\tikz[remember picture] \node[] (callbr) {};!
    move  rtmp1 pc
    cca   rtmp1 -20
\end{lstlisting}&
\begin{lstlisting}[basicstyle=\tiny\ttfamily,escapechar=!]
    load  rtmp1 rtmp1
    cca   rtmp1 -21
    cseal rretd rtmp1
    move  rretc pc
   !\tikz[remember picture] \node[] (retl) {};!xjmp  r1 r2 !\tikz[remember picture] \node[] (retr) {};!
    cseal rretc rtmp1
    move  rtmp1 0    !\tikz[remember picture] \node[] (srccodebr) {};!
\end{lstlisting}
\end{tabular}\tikz[remember picture] \node[] (srcr) {};\\
\onslide<2->{\hdashrule[0.1ex]{12cm}{1pt}{5pt}}
\\\begin{tabular}{p{3.2cm} p{3.2cm}}
\begin{lstlisting}[basicstyle=\tiny\ttfamily]
    move  rtmp1 42
    store rstk rtmp1
    cca   rstk -1
    geta  rtmp1 rstk
    cca   rretc 5
    move  rtmp1 pc
    cca   rtmp1 -20
\end{lstlisting}&
\begin{lstlisting}[basicstyle=\tiny\ttfamily]
    load  rtmp1 rtmp1
    cca   rtmp1 -21
    cseal rretd rtmp1 
    move  rretc pc
    xjmp  r1 r2
    cseal rretc rtmp1
    move  rtmp1 0
\end{lstlisting}
\end{tabular}\tikz[remember picture] \node[] (trgr) {};
    \begin{tikzpicture}[remember picture, overlay]
      %White overlay
      \draw<1> node[rectangle,fit=(srccodetl) (srccodebr), fill=white] (whiteoverlay) {};

@@

      % LCM text
      \draw node[right = 3.3cm of trgr, text width = 3cm] {Linear Capability Machine (LCM)};

      % Call stack
      % TODO draw call stack
      \begin{scope}
        \clip<3-> ($(srcr) + (0.1,-1.2)$) rectangle ($(srcr) + (2.1,-.75)$);
        \draw<3-> ($(srcr) + (0.2,-1.5)$) rectangle ($(srcr) + (2,-.75)$) node[pos=.5,align=center] {\scriptsize{...}};
      \end{scope}
      \draw<3-> ($(srcr) + (0.2,-0.75)$) rectangle ($(srcr) + (2,-0.25)$) node[pos=.5,align=center] {\scriptsize{frame 1}};
      \draw<3-> ($(srcr) + (0.2,-0.25)$) rectangle ($(srcr) + (2,0.25)$) node[pos=.5,align=center] {\scriptsize{frame 2}};
      \draw<3-> ($(srcr) + (0.2,.25)$) rectangle ($(srcr) + (2,.75)$) node[pos=.5,align=center] {\scriptsize{frame 3}};

      \draw<3-> ($(srcr) + (1.1,1.25)$) node[align=center] {\footnotesize{Builtin call stack}};
      \draw<3-> ($(srcr) + (0.2,-.75)$) -- ($(srcr) + (0.2,-1)$);
      \draw<3-> ($(srcr) + (2,-.75)$) -- ($(srcr) + (2,-1)$);
      % Return red overlay
      \draw<4-> node[rectangle, fit=(retl) (retr),fill={rgb:red,192;green,58;blue,45},fill opacity=0.6, rounded corners] (ret) {};
      \draw<4-> node[rectangle, fit=(retl) (retr)] (rettext) [yshift=-0.1cm] {\textbf{\texttt{return}}};

      %oLCM text
      \draw<2-> node[right = 3.3cm of srcr, text width = 3cm] {Overlay Semantics (oLCM)};
%      \draw[dashed] (mid) -- ($(mid) + (7,0)$);
    \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Fully-abstract overlay semantics}
  \begin{columns}
\begin{column}{0.5\textwidth}
  \begin{itemize}[<+->]
  \item Compile from oLCM to LCM
  \item Compilation is the identity
  \item Builtin call stack abstraction in oLCM preserved after compilation
  \end{itemize}
\end{column}
\begin{column}{0.5\textwidth}
  \begin{tikzpicture}
    \draw (0,0) node[draw=black, rounded corners] (olcm) {oLCM};
    \draw node[draw=black, rounded corners,below=2.5cm of olcm] (lcm) {LCM};
    \draw (olcm) edge[bend left, ->,thick] (lcm);
    \draw node[left = 3cm of olcm] (ll1) {};
    \draw node[right = 3cm of olcm] (rl1) {};
    \draw node[below = 1.25cm of ll1] (ll) {};
    \draw node[below = 1.25cm of rl1] (rl) {};
    \draw[dashed] (ll) -- (rl);

    \draw<1> (olcm) edge[bend left, ->,thick] node[right, near start] { } (lcm);
    \draw<2-> (olcm) edge[bend left, ->,thick] node[right, near start] {$id$} (lcm);
  \end{tikzpicture}
\end{column}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{Evaluating the definition}
  \begin{enumerate}
  \item {\itshape Intuitive}\\
    \onslide<2->{Yes, call stack corresponds exactly to our intuition.}
\item {\itshape Useful for reasoning}\\% we should be able to use WBCF and LSE
                                % when reasoning about correctness and security
                                % of programs using \stktokens{}.
  \onslide<3->{Yes, ...}
\item {\itshape Reusable in secure compiler chains}\\% for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.
  \onslide<4->{Yes, fully-abstract compilations compose vertically, so oLCM can
    be used as a target for other compilation phases.}
\item {\itshape Arguably "complete"}\\% the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. 
  \onslide<5->{Yes, ...}
%\item {\itshape potentially scalable}% although dynamic code generation and multi-threading are currently out of scope, the formalization should, at least potentially, extend to such settings.
\end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{The \stktokens{} calling convention}
  \begin{onslide}<2->
    ... is explained in the paper.
  \end{onslide}
\end{frame}

>>>>

\usepackage{appendixnumberbeamer}
\usepackage{xcolor}
\input{preamble}
\input{../illustrations/preamble}

@@

    \begin{onlyenv}<7->
      \draw (0.8, 3.7) edge[-stealth,out=25,in=155,very thick,align=center,color=white] node[above] {{\color{myred} secure}\\compilation} (4.3, 3.7);
      \draw node[rectangle,fill=white,draw] at (1.93,3.7) (ir1) {...};
      \draw node[rectangle,fill=white,rounded corners,draw] at (3.15,3.7) (ir2) {ir};
      \draw (0.8, 3.7) edge[-stealth,bend left,very thick] node[above] {} (ir1);
      \draw (ir1) edge[-stealth,bend left,very thick] node[above] {} (ir2);
      \draw (ir2) edge[-stealth,bend left,very thick] node[above] {} (4.3,3.7);
    \end{onlyenv}

@@

% Secure compilations: If security properties in target can be proven in source.

@@

%\section{Paper Overview}
% \begin{frame}
%   \frametitle{Linear capability machine}
%   \begin{columns}
% \begin{column}{0.5\textwidth}
%   \begin{itemize}
%   \item<1-> Low-level machine
%     \note<1->[item]{Capability machines are low-level machines proposed in the systems community.}
%     \note<1->[item]{For instance, the CHERI OS operates on one.}
%     \note<1->[item]{Has all the instructions we expect, load, store, jmp, etc.}
%     % \note{Has instructions as you would expect, load, store, jmp, etc.}
%   \item<2-> Capabilities replace pointers
%     \begin{itemize}
%     \item<3-> Pointer
%     \item<4-> Range of authority
%     \item<5-> Kind of authority
%       \note<5->[item]{Roughly two kinds of capabilities:}
%       \begin{itemize}
%       \item read, write, and execute
%         \note<5->[item]{Memory capabilities, allows you to do all the standard memory operations.}
%       \item sealed
%         \note<5->[item]{Provides encapsulation mechanism which allows seperation of security domains.}
%         \note<5->[item]{Can not be used for anything but jump, when jumped to becomes read/execute.}
%       \end{itemize}
%     \end{itemize}
%     \item<6-> Capability manipulation instructions
%     \item<7-> Authority checked dynamically
%     \item<8-> Linear capabilities non-copyable
%       \begin{itemize}
%       \item<9-> Split and splice instructions
%       \end{itemize}
%     \end{itemize}
% \end{column}

% \begin{column}{0.5\textwidth}
%   \begin{tikzpicture}[scale=.5, every node={scale=.5}]
%     \draw (1,9) node {Memory};
%     \draw (-3.5,0) node {\phantom{.}};
%     \scope
%       \clip (-.1,-.1) rectangle (6.1,8.1);
%       \fill[fill=white] (0,0) rectangle (6,8);
%       \draw (0,0) -- (0,8);
%       \draw (6,0) -- (6,8);
%     \endscope
%     % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);
%     \draw (-1.5,0) node {};
%     \draw (-1.5,8) node {};
%     \foreach \x in {0.5,1,...,7}
%     {
%       \draw[fill=white] (0,\x) rectangle (6,\x+.5) node[pos=.5,color=teal] {};
%     };

%     \draw<3>  (-3,1.5) edge[black,->,in=180] (0,2.75);

%     \draw<4-9> [decorate,decoration={brace,amplitude=3pt,raise=0pt},yshift=0pt]
%     (-0.25,1) -- (-0.25,4.5) node[draw=black] (sp1) [black,midway,xshift=-12pt] {};
%     \draw<4>  (-3,1.5) edge[black,->,in=180] node[above left]
%     {\footnotesize\phantom{\textsc{rw}}} (sp1);
%     \draw<5-7>  (-3,1.5) edge[black,->,in=180] node[above left] {\footnotesize \textsc{rw}} (sp1);

%     \draw<8-9>  (-3,1.5) edge[black,->,in=180, dashed] node[above left] {\footnotesize \textsc{rw}} (sp1);

%     \draw<10> [decorate,decoration={brace,amplitude=3pt,raise=0pt},yshift=0pt]
%     (-0.25,1) -- (-0.25,2.5) node[draw=black] (sp2) [black,midway,xshift=-12pt] {};
%     \draw<10> [decorate,decoration={brace,amplitude=3pt,raise=0pt},yshift=0pt]
%     (-0.25,2.5) -- (-0.25,4.5) node[draw=black] (sp3) [black,midway,xshift=-12pt] {};
%     \draw<10>  (-3,2) edge[black,->,in=180, dashed] node[above left] {\footnotesize \textsc{rw}} (sp3);
%     \draw<10>  (-3,1) edge[black,->,in=180, dashed] node[below right] {\footnotesize \textsc{rw}} (sp2);

%     \draw<11-> [decorate,decoration={brace,amplitude=3pt,raise=0pt},yshift=0pt]
%     (-0.25,1) -- (-0.25,4.5) node[draw=black] (sp1) [black,midway,xshift=-12pt] {};
%     \draw<11->  (-3,1.5) edge[black,->,in=180, dashed] node[above left] {\footnotesize \textsc{rw}} (sp1);
%   \end{tikzpicture}
% \end{column}
% \end{columns}
% \end{frame}
\section{Capability machines and \stktokens{}}

\input{../illustrations/traditional}
\input{../illustrations/capabilities}
\begin{frame}
    \frametitle{\stktokens{} prevent the attack}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (16.5,5.5) node {register file};
    \begin{scope}
      \clip (15.9,1.1) rectangle (17.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (16,\x) rectangle (17,\x+1) node[pos=.5,color=teal] {};
      };
    \end{scope}
    \node (r1) at (16.75,4.5) {};
    \node (r2) at (16.75,3.6) {};

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (r1) edge[->,red,thick,bend left] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw (r2) edge[->,red,thick,bend left] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,thick,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,red,bend left] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { \phantom{return data pointer} };
      \draw node[right=0cm of sp2] { return data pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}
    \draw<.-> (r2) edge[->,red,bend left] (sp2);

    \begin{onlyenv}<.->
      \begin{scope}
        \fill[gray!20] (14,9) rectangle (18,14);
        \draw (14,9) -- (14,14);
        \draw (18,9) -- (18,14);
      \end{scope}
    \end{onlyenv}
    \draw<.>[fill=white] (14,10) rectangle node[color=red] {} (18,10.5);

    % Callee stores stack pointer
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (8,5) -- (8,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (16,15) node {heap memory};
    \end{onlyenv}

    \begin{onlyenv}<.>
      \draw (14,10.25) edge[->,red,thick,bend right] (usp);
      \draw[fill=white] (14,10) rectangle node[color=red] {\scriptsize old sp} (18,10.5);
      \draw node[right=0cm of usp] { stack pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { \phantom{return data pointer} };
      \draw node[right=0cm of sp2] { return data pointer };
    \end{onlyenv}

    % Return from callee
    \begin{onlyenv}<+->
      \draw (14,10.25) edge[->,red,bend right] (usp);
      \draw[fill=gray!50] (14,10) rectangle node[color=red] {\scriptsize old sp} (18,10.5);
      \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[right=0cm of sp2] { private stack pointer };
      \draw node[right=0cm of usp] { stack pointer };
    \end{onlyenv}

    \draw<+>[teal,very thick] (6.4,4.4) -- (7.4,5.4);
    \draw<.>[teal,very thick] (7.4,4.4) -- (6.4,5.4);
    \draw<.> node[teal,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (14,4) { Splice fails,\\ stack pointer is linear!};  
  \end{tikzpicture}  
\end{frame}

% \begin{frame}
%   \frametitle{\stktokens{}}
%  \begin{itemize}
%  \item Use linear capability for stack.
% \item On call, split off local stack frame and encapsulate it.
% \item   On return, require that the local stack frame is returned.
% \item   The encapsulated stack frame works like a token that permits you to return. You must use the token when returning.
% \item   A good number of details to get right - see the paper.
%    \end{itemize}
% \end{frame}

\section{Defining well-bracketed control flow and local state encapsulation by fully-abstract overlay semantics}
\begin{frame}[fragile]
  \frametitle{Well-bracketed control flow and local state encapsulation}
  \begin{columns}
    \begin{column}{0.5\textwidth}
\begin{lstlisting}[language=C, escapechar=!]
!\tikz[remember picture] \node[] (a) {};!void a()       !\tikz[remember picture] \node[] (bt) {};! 
 {
   !\tikz[remember picture] \node[] (pc6) {};!...
   !\tikz[remember picture] \node[] (pc7) {};!return;!\tikz[remember picture] \node[] (ret) {};!      
 }              !\tikz[remember picture] \node[] (bb) {};!

 void b()
 {
   !\tikz[remember picture] \node[] (pc1) {};!int x = 5;
   !\tikz[remember picture] \node[] (pc2) {};!a();
   !\tikz[remember picture] \node[] (pc3) {};!...
   !\tikz[remember picture] \node[] (pc4) {};!a();
   !\tikz[remember picture] \node[] (pc5) {};!return;   
 }
\end{lstlisting}
% Mention that our work support high-order
% No good definition. We appeal to you intuitive definition
      \begin{tikzpicture}[remember picture, overlay]
%        \draw<1> node { };
        \draw<2>[decorate,decoration={brace,amplitude=6pt,raise=4pt},yshift=0pt] ($(bt) + (0,0.2)$) -- ($(bb) + (0,-0.2)$) node[xshift=0.2cm] (brace) [midway] {};
        \draw<2> node[right = -0cm of brace, text width = 3cm] {Function \texttt{a} cannot access variable \texttt{x}};

        \draw<3> ($(pc4) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc4);
        \draw<4> ($(a) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (a);
        \draw<5> ($(pc6) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc6);
        \draw<6> ($(pc7) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc7);
        \draw<7-> node[below right = of ret] (w) {\huge ?};
        \draw<7-> (ret) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202},bend left] (w);
        \draw<8> ($(pc5) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc5);
        \draw<9> ($(pc3) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc3);
      \end{tikzpicture}
    \end{column}
    \begin{column}{0.5\textwidth}
      \only<2>{Local-state encapsulation (LSE)}
      \only<3->{Well-bracketed control flow (WBCF)}
    \end{column}
    % What is LSE and WBCF
    % Quick example?
  \end{columns}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Fully-abstract overlay Semantics}
\onslide<8->{\hdashrule[0.1ex]{12cm}{1pt}{5pt}}
\begin{tabular}{p{3.2cm} p{3.2cm}}
\begin{lstlisting}[basicstyle=\tiny\ttfamily,escapechar=!]
   !\tikz[remember picture] \node[] (srccodetl) {};!move  rtmp1 42
   !\tikz[remember picture] \node[] (calltl) {};!store rstk rtmp1
    cca   rstk -1
    geta  rtmp1 rstk
    cca   rretc 5      !\tikz[remember picture] \node[] (callbr) {};!
    move  rtmp1 pc
    cca   rtmp1 -20
\end{lstlisting}& \tikz[remember picture] \node[] (srcm) {};
\begin{lstlisting}[basicstyle=\tiny\ttfamily,escapechar=!]
    load  rtmp1 rtmp1
    cca   rtmp1 -21
    cseal rretd rtmp1
    move  rretc pc
   !\tikz[remember picture] \node[] (retl) {};!xjmp  r1 r2 !\tikz[remember picture] \node[] (retr) {};!
    cseal rretc rtmp1
    move  rtmp1 0    !\tikz[remember picture] \node[] (srccodebr) {};!
\end{lstlisting}
\end{tabular}\tikz[remember picture] \node[] (srcr) {};\\
\onslide<2->{\hdashrule[0.1ex]{12cm}{1pt}{5pt}}
\\\begin{tabular}{p{3.2cm} p{3.2cm}}
\begin{lstlisting}[basicstyle=\tiny\ttfamily]
    move  rtmp1 42
    store rstk rtmp1
    cca   rstk -1
    geta  rtmp1 rstk
    cca   rretc 5
    move  rtmp1 pc
    cca   rtmp1 -20
\end{lstlisting}& \tikz[remember picture] \node[] (trgm) {};
\begin{lstlisting}[basicstyle=\tiny\ttfamily]
    load  rtmp1 rtmp1
    cca   rtmp1 -21
    cseal rretd rtmp1 
    move  rretc pc
    xjmp  r1 r2
    cseal rretc rtmp1
    move  rtmp1 0
\end{lstlisting}
\end{tabular}\tikz[remember picture] \node[] (trgr) {};
    \begin{tikzpicture}[remember picture, overlay]
      %White overlay
      \draw<1> node[rectangle,fit=(srccodetl) (srccodebr), fill=white] (whiteoverlay) {};

@@

      % LCM text
      \draw node[right = 3.3cm of trgr, text width = 3cm] {Linear Capability Machine};

      % Call stack
      \begin{scope}
        \clip<3-> ($(srcr) + (0.1,-1.2)$) rectangle ($(srcr) + (2.1,-.75)$);
        \draw<3-> ($(srcr) + (0.2,-1.5)$) rectangle ($(srcr) + (2,-.75)$) node[pos=.5,align=center] {\scriptsize{...}};
      \end{scope}
      \draw<3-> ($(srcr) + (0.2,-0.75)$) rectangle ($(srcr) + (2,-0.25)$) node[pos=.5,align=center] {\scriptsize{frame 1}};
      \draw<3-> ($(srcr) + (0.2,-0.25)$) rectangle ($(srcr) + (2,0.25)$) node[pos=.5,align=center] {\scriptsize{frame 2}};
      \draw<3-> ($(srcr) + (0.2,.25)$) rectangle ($(srcr) + (2,.75)$) node[pos=.5,align=center] {\scriptsize{frame 3}};

      \draw<3-> ($(srcr) + (1.1,1.25)$) node[align=center] {\footnotesize{Builtin call stack}};
      \draw<3-> ($(srcr) + (0.2,-.75)$) -- ($(srcr) + (0.2,-1)$);
      \draw<3-> ($(srcr) + (2,-.75)$) -- ($(srcr) + (2,-1)$);

      % Return red overlay
      \draw<4-> node[rectangle, fit=(retl) (retr),fill={rgb:red,192;green,58;blue,45},fill opacity=0.6, rounded corners] (ret) {};
      \draw<4-> node[rectangle, fit=(retl) (retr)] (rettext) [yshift=-0.1cm] {\textbf{\texttt{return}}};

      %oLCM text
      \draw<2-> node[right = 3.3cm of srcr, text width = 3cm] {Overlay Semantics};
      % \draw[dashed] (mid) -- ($(mid) + (7,0)$);

      % Compilation, no id
      \draw<5> ($(srcm) + (-0.3,-1)$) edge[bend left, -stealth, very thick] ($(trgm) + (-0.3,-1)$);

      % Compilation with id
      \draw<6-> ($(srcm) + (-0.3,-1)$) edge[bend left, -stealth, very thick] node[right] {$id$} ($(trgm) + (-0.3,-1)$);

      % Call stack
      \begin{scope}
        \clip<7-> ($(trgr) + (0.1,-1.2)$) rectangle ($(trgr) + (2.1,-.75)$);
        \draw<7-> ($(trgr) + (0.2,-1.5)$) rectangle ($(trgr) + (2,-.75)$) node[pos=.5,align=center] {\scriptsize{...}};
      \end{scope}
      \draw<7-> ($(trgr) + (0.2,-0.75)$) rectangle ($(trgr) + (2,-0.25)$) node[pos=.5,align=center] {\scriptsize{frame 1}};
      \draw<7-> ($(trgr) + (0.2,-0.25)$) rectangle ($(trgr) + (2,0.25)$) node[pos=.5,align=center] {\scriptsize{frame 2}};
      \draw<7-> ($(trgr) + (0.2,.25)$) rectangle ($(trgr) + (2,.75)$) node[pos=.5,align=center] {\scriptsize{frame 3}};

      \draw<7-> ($(trgr) + (1.1,1.25)$) node[align=center] {\footnotesize{Builtin call stack}};
      \draw<7-> ($(trgr) + (0.2,-.75)$) -- ($(trgr) + (0.2,-1)$);
      \draw<7-> ($(trgr) + (2,-.75)$) -- ($(trgr) + (2,-1)$);
      \fill<7->[white,opacity=0.75] ($(trgr) + (-.1,1.5)$) rectangle($(trgr) + (2.5,-1.25)$);

      % Higher compilations
      \draw<8> ($(srcm) + (0.2,0.65)$) edge[-stealth,out=-90,in=45,very thick,align=center] ($(srcm) + (-0.3,-0.9)$);
    \end{tikzpicture}
\end{frame}

% \begin{frame}
%   \frametitle{Fully-abstract overlay semantics}
%   \begin{columns}
% \begin{column}{0.5\textwidth}
%   \begin{itemize}[<+->]
%   \item Compile from oLCM to LCM
%   \item Compilation is the identity
%   \item Builtin call stack abstraction in oLCM preserved after compilation
%   \end{itemize}
% \end{column}
% \begin{column}{0.5\textwidth}
%   \begin{tikzpicture}
%     \draw (0,0) node[draw=black, rounded corners] (olcm) {oLCM};
%     \draw node[draw=black, rounded corners,below=2.5cm of olcm] (lcm) {LCM};
%     \draw (olcm) edge[bend left, ->,thick] (lcm);
%     \draw node[left = 3cm of olcm] (ll1) {};
%     \draw node[right = 3cm of olcm] (rl1) {};
%     \draw node[below = 1.25cm of ll1] (ll) {};
%     \draw node[below = 1.25cm of rl1] (rl) {};
%     \draw[dashed] (ll) -- (rl);

%     \draw<1> (olcm) edge[bend left, ->,thick] node[right, near start] { } (lcm);
%     \draw<2-> (olcm) edge[bend left, ->,thick] node[right, near start] {$id$} (lcm);
%   \end{tikzpicture}
% \end{column}
% \end{columns}
% \end{frame}

% \begin{frame}
%   \frametitle{Evaluating the definition}
%   \begin{enumerate}
%   \item {\itshape Intuitive}\\
%     \onslide<2->{Yes, call stack corresponds exactly to our intuition.}
% \item {\itshape Useful for reasoning}\\% we should be able to use WBCF and LSE
%                                 % when reasoning about correctness and security
%                                 % of programs using \stktokens{}.
%   \onslide<3->{Yes, ...}
% \item {\itshape Reusable in secure compiler chains}\\% for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.
%   \onslide<4->{Yes, fully-abstract compilations compose vertically, so oLCM can
%     be used as a target for other compilation phases.}
% \item {\itshape Arguably "complete"}\\% the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. 
%   \onslide<5->{Yes, ...}
% %\item {\itshape potentially scalable}% although dynamic code generation and multi-threading are currently out of scope, the formalization should, at least potentially, extend to such settings.
% \end{enumerate}
% \end{frame}

% \begin{frame}
%   \frametitle{The \stktokens{} calling convention}
%   \begin{onslide}<2->
%     ... is explained in the paper.
%   \end{onslide}
% \end{frame}

\begin{frame}
  \frametitle{Paper overview}
\begin{itemize}
\item LCM: A formalization of a simple CHERI-like capability machine with linear capabilities
\item \stktokens{}, a new calling convention that provably guarantees LSE and WBCF on LCM
\item A new way to formalize these guarantees based on a novel technique called \textit{fully-abstract overlay semantics}
\item Proof of LSE and WBCF which includes
  \begin{itemize}
  \item oLCM: an overlay semantics for LCM with built-in LSE and WBCF
  \item proving full-abstraction for the embedding of oLCM into LCM by
  \item defining and using a cross-language, step-indexed, Kripke logical relation with recursive worlds
  \end{itemize}
\end{itemize}
  % \begin{description}
  % \item[Formalization of CHERI-like capability machine with linear capabilities]
  % \item[\stktokens{}] a calling convention that provably guarantees LSE and well-bracketed control-flow WBCF
  % \item[Fully-abstract overlay semantics] a novel way to prove LSE and WBCF claims
  %   \begin{itemize}
  %   \item Proven with cross-language logical relations
  %   \end{itemize}
  %   % TODO Mention the proof and logical relation, move to end?
  % \end{description}
\end{frame}
